The Country-level Impact of Educational Patterns on the Rate of Entrepreneurship

### 2014-11-10 Proposal/EducProposal.Rmd
revised data set

---
title: "The Country-level Impact of Educational Patterns on the Rate of Entrepreneurship"
author: "Sam Dundon and Thierry Racaud"
date: "October 24, 2014"
output: pdf_document
bibliography: Main.bib
---
* * * 
```{r echo=FALSE, cache=TRUE, include=FALSE}
# Set working directory
setwd('~/Assign2Education/')

>>>>

---
title: "The Country-level Impact of Educational Patterns on the Rate of Entrepreneurship"
author: "Sam Dundon and Thierry Racaud"
date: "October 24, 2014"
output: word_document
bibliography: Main.bib
---
* * * 
```{r echo=FALSE, cache=TRUE, include=FALSE}
# Set working directory
setwd('~/Assign2Education/Proposal')
